---
title: "EDA"
author: "Echo"
date: "05/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Lets use this R chunk to load required libraries and set project working directory

# This library is used for formating text (bold, color, font, size etc)
#install.packages("kableExtra")
library(kableExtra)

# set working directory
setwd("D:\\HeadFirst\\Data Science\\data set")
```

We will use IMDB data set which has data about 5000 movies.
Using this dataset we will solve some of the task given below to cover today's topic.

1. `r text_spec("know top 10 movies which  have the highest profit ?", color = "blue")`
2. `r text_spec("Know top rated movies in the list and also average IMDB score ?", color = "blue")`
3. `r text_spec("Plot a graphical representation to show number of movies release each year ?", color = "blue")`

## Phase 1 : DATA ACQUISITION
In this phase, based on the source from where we have to gather data, we write R code to acquire them.

*So of the type of acquisition can be from:*

1. CSV(at rest)
2. CSV(from web)
3. Excel
4. MySQL database
5. WebScraping (unstructured)
6. XML
7. JSON
8. API

Let's now write command to acquire the data from above source types

```{r}
# Load CSV file from WEB
url = "https://people.sc.fsu.edu/~jburkardt/data/csv/deniro.csv"
download.file(url, destfile = "deniro.csv")

camera_data = read.csv("deniro.csv", header = TRUE)
head(camera_data)
```


```{r}
# Load Excel Files
# install.packages("readxl")
library(readxl)

setwd("D:\\HeadFirst\\Data Science\\data set")
movie_data = read_xlsx("movie_metadata_excel.xlsx", sheet = "movie_metadata")
head(movie_data)

```

```{r}

# Load CSV file rest 
movie_data = read.csv("movie_metadata.csv", header = TRUE)
str(movie_data)

my_dataframe = as.data.frame(matrix(nrow = 3, ncol = 4)) 

```




We have now acquired the raw data, we will have to now make sure that data is clean and thus prepare it for modelling.

###############################################################################################################################################

## Phase 2 : DATA PREPERATION 

This phase has multiple sub-phases like :

1.**Data Wrangling** : Here we do cleaning, standardizing, derive, or remove unwanted columns.
          + Data subsetting -> Create a new dataset out of existing dataset.
          + Data filtering 
          + Removing null values
          + Text Manipulation

2. **Data Exploration** : Here we explore and understand data.
          + Find number of rows and columns in dataset.
          + Understand and display initial top and last records of dataset.
          + Understand and display names of columns.
          + Understand the structure of columns.
          + Display all the records of dataset.
          
3. **Data Visualization** : Here we do visual representation of data.
          + Boxplot
          + Histogram
          + Scatter plot 

## Data Wrangling 
```{r}
# Give dimension of dataframe
dim(movie_data) 
# TO find column names 
names(movie_data) 
colnames(movie_data)
# To find data of specific index
# movie_data[row, column]
movie_data[, "director_name"]
movie_data[ , c("actor_2_name", "director_name", "gross")]

color_movie = movie_data[movie_data[ , "color"]=="Color", ]
color_movie = movie_data[movie_data$color=="Color", ]

temp1 = movie_data[,2:5]
names(temp1)
head(temp1)
dim(temp1)

temp2 = movie_data[2:5, 2:5]
names(temp2)
head(temp2)
dim(temp2)
```

```{r}

# Cleaning : Removing records which have NA(Blank)

# Identifying if dataset have NA
anyNA(movie_data)

# Which cells have NA
head(is.na(movie_data))

# Identify which column have how many NA's
colSums(is.na(movie_data))

# Missing value treatment
movie_data_clean = na.omit(movie_data)
dim(movie_data_clean)
str(movie_data_clean)
```

```{r}

head(movie_data_clean)
# Text Manipulation
head(movie_data_clean$movie_title)

# remove unwanted text from dataset
movie_data_clean$movie_title = sub(pattern = "Â", replacement = "", x = movie_data_clean$movie_title)

head(movie_data_clean$movie_title)
head(trimws(movie_data_clean$movie_title))

class(movie_data_clean$movie_title)

#movie_data_clean$movie_title =trimws(movie_data_clean$movie_title, which = "both")
```

## Data Exploration 

```{r}
# Write R code for data exploration/ analysis

dim(movie_data_clean)

nrow(movie_data_clean)
ncol(movie_data_clean)

head(movie_data_clean)
tail(movie_data_clean)

names(movie_data_clean)

str(movie_data_clean)

?levels
levels(movie_data_clean)

summary(movie_data_clean)
```

# Now to solve our problems
1. `r text_spec("Know top 10 movies with the highest profit?", color="blue")`

```{r}
# We will take the cleaned dataset

str(movie_data_clean)

movie_data_clean$profit_loss = movie_data_clean$gross - movie_data_clean$budget
head(movie_data_clean$profit_loss, 10)

movie_data_clean = movie_data_clean[order(-movie_data_clean$profit_loss), ]  
head(movie_data_clean)  

head(cbind(movie_data_clean$movie_title, movie_data_clean$profit_loss),10)

```


2. `r text_spec("Know the top rated movie in the list and also average IMDB score?", color = "blue")`

```{r}

# Top 10 movies my IMDB rating/score
movie_data_clean = movie_data_clean[order(-movie_data_clean$imdb_score), ]
head(cbind(movie_data_clean$movie_title, movie_data_clean$imdb_score), 10)

# Average IMDB rating

mean(movie_data_clean$imdb_score)

```

## Data Visualization

```{r}
# Boxplot
boxplot(movie_data_clean$imdb_score, horizontal = TRUE)

```



```{r}
# Histogram

hist(movie_data_clean$title_year)

```


```{r}
# Scatter plot

plot(movie_data_clean$duration)

plot(movie_data_clean$gross, movie_data_clean$budget)

```


3. `r text_spec("Plot a graphical repersentation to show number of movies release each year?", color = "blue")`

```{r}

# Write R code for visualization
# Histogram
max(movie_data_clean$title_year, na.rm = TRUE)
min(movie_data_clean$title_year, na.rm = TRUE)
m_break = seq(min(movie_data_clean$title_year, na.rm = TRUE), max(movie_data_clean$title_year, na.rm = TRUE), by = 1)

hist(movie_data_clean$title_year, breaks = m_break)
hist_data = hist(movie_data_clean$title_year, breaks = m_break)

# Index of years where highest movies 
# temp = hist_data[order(-hist_data$counts), ]
which.max(hist_data$count)
hist_data$mids[82]

```












































