---
title: "LinearRegression"
author: "Echo"
date: "02/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Linear Regression Modal
```{r}
library(MASS)
#data(Boston)
boston_data = Boston
names(boston_data)
help(Boston)
  # crim: per capita crime rate by town.
  # zn: proportion of residential land zoned for lots over 25,000 sq.ft.
  # indus: proportion of non-retail business acres per town.
  # chas: Charles River dummy variable (= 1 if tract bounds river; 0 otherwise).
  # nox: nitrogen oxides concentration (parts per 10 million).
  # rm: average number of rooms per dwelling.
  # age: proportion of owner-occupied units built prior to 1940.
  # dis: weighted mean of distances to five Boston employment centres.
  # rad: index of accessibility to radial highways.
  # tax: full-value property-tax rate per \$10,000.
  # ptratio: pupil-teacher ratio by town.
  # black: 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town.
  # lstat: lower status of the population (percent).
  # medv: median value of owner-occupied homes in \$1000s.

names(boston_data$crim) = "per_capita_crime_rate"
names(boston_data) = c("per_capita_crime_rate", "residential_zone_prop", "industrial_prop",
                       "charles_river_tract", "nitrous_oxide_conc", "avg_rooms_per_home",
                       "owner_age_prop", "weighted_distance_employment_center",
                       "access_to_radial_highways_index", "property_tax_rate_per_10k",
                       "pupil_teacher_ratio", "African_American_prop", "lower_status_population_percentage",
                       "media_owner_occupied_home_in_1k"
                       )
names(boston_data)
str(boston_data)
summary(boston_data)
boston_data$charles_river_tract = as.factor(boston_data$charles_river_tract)
dim(boston_data)
```


#Bivariate analysis : Strength of relationship
```{r}
library(corrplot)
numeric_dataset = boston_data[-4] # removing the charles_river_tract column because it is a categorical variable
cor(numeric_dataset)

corrplot(cor(numeric_dataset),method = "number", type = "lower") 

```

# Train & Test Dataset
```{r}
library(caTools)
set.seed(1234)
index = sample.split(boston_data, SplitRatio = 0.7)
training_data = subset(boston_data, index==TRUE)
testing_data = subset(boston_data, index==FALSE)

dim(boston_data)
dim(training_data)
dim(testing_data)

```

# Linear model
```{r}
names(training_data)
library(cars)
# lm is the algorithm used to create a linear regression model 
linear_model = lm(media_owner_occupied_home_in_1k~., training_data)
#we write "." after tilda to create our model with all the variables but if we want to create it with only a few we can write then using + after tilda
summary(linear_model)

linear_model_1 = lm(media_owner_occupied_home_in_1k~.
                                                    -industrial_prop
                                                    -charles_river_tract
                                                    -owner_age_prop,
                    training_data
                    )
summary(linear_model_1)
```


# Linear model : Back-tracking validation
```{r}
pred_train_medv = predict(linear_model, training_data)
head(pred_train_medv)

plot(training_data$media_owner_occupied_home_in_1k, type="l",col="green")
lines(pred_train_medv, col="blue")

```


# Training Dataset : Model performance : Back-tracing
```{r}
library(Metrics)
trained_mse = mse(training_data$media_owner_occupied_home_in_1k, pred_train_medv)
trained_rmse = rmse(training_data$media_owner_occupied_home_in_1k, pred_train_medv)
trained_mape = mape(training_data$media_owner_occupied_home_in_1k, pred_train_medv)

trained_r2 = summary(linear_model)$r.squared

training_model_perf = cbind(Dataset = "TrainingDS",
                            MSE = round(trained_mse,3),
                            RMSE = round(trained_rmse,3),
                            MAPE = round(trained_mape,3),
                            R2 = round(trained_r2,3)
                            )

training_model_perf
```

# Linear model - Prediction based on unknown - (Testing Dataset)

```{r}
#using test data 
pred_test_medv = predict(linear_model, testing_data)

```

# Compare actual vs predict test data values
```{r}
plot(testing_data$media_owner_occupied_home_in_1k, type = "l", col="green")
lines(pred_test_medv, col = "blue")

```


# Testing Dataset : Model performance : Evaluation
```{r}
test_mse = mse(testing_data$media_owner_occupied_home_in_1k, pred_test_medv)
test_rmse = rmse(testing_data$media_owner_occupied_home_in_1k, pred_test_medv)
test_mape = mape(testing_data$media_owner_occupied_home_in_1k, pred_test_medv)

test_r2 = cor(testing_data$media_owner_occupied_home_in_1k, pred_test_medv)^2
testing_model_perf = cbind(Dataset = "TestDS",
                           MSE=round(test_mse,3),
                           RMSE=round(test_rmse,3),
                           MAPE=round(test_mape,3),
                           R2=round(test_r2,3)
                           )
testing_model_perf
```

# Compare Training vs Testing Dataset : Model performance
```{r}
rbind(training_model_perf, testing_model_perf)
```
z












