---
title: "RecommendationEngine"
author: "Echo"
date: "11/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#########################################################################################################################################################
# ASSOCIATION RULES 
# Add the required libraries 
```{r}
# install.packages("arules")
library(arules)

```

# Read the groceries transactional data 
```{r}

groceries = read.transactions("groceries.csv", sep = ",")
groceries

```

# Understand the transaction grocery 
```{r}

summary(groceries)

```

# Read the transactional items
```{r}

# TOO large avoid executing 
# inspect(groceries)

inspect(groceries[1:10])

```


# Identify the support values for certain item 
```{r}

itemFrequency(groceries[, 1]) #single item

itemFrequency(groceries[,1:10]) # multiple items

# Vizualisation

itemFrequencyPlot(groceries, support = 0.08)
itemFrequencyPlot(groceries, topN = 5)

```


# Getting Association Rules using apriori function

## Default Run 
```{r}

basket1 = apriori(groceries) # default support of 0.1 and confidance of 0.80
summary(basket1)
class(basket2)



```


## Default Run 
```{r}

basket2 = apriori(groceries, parameter = list(support = 0.007, confidence = 0.5))
summary(basket2)

# Find out a few of the association rule based on above filter
inspect(basket2[1:3])

# Displaying sorted association rule by descendeing order of lift
inspect(sort(basket2, by = "lift")[1:5])

```

# Find out Items purchased AFTER customers had "milk and soda " already in their basket 
```{r}

basket3 = apriori(groceries, parameter = list(support = 0.007, confidence = 0.2),
                  appearance = list(default="rhs", lhs = c("whole milk", "soda")))

inspect(basket3[1:9])

```

## Visulization of association rule 
```{r}

# install.packages("arulesviz")
library(arulesViz)
plot(basket3)

```


#####################################################################################################################################################

# RECOMMENDATION ENGINES 

##########################################3

1. User Based Collaborative Filtering (UBCF)
2. Content Based Filtering (CBF)

## Recommendation Engine library 
```{r}

# install.packages("recommenderlab")
library(recommenderlab)

```

## Load Jester5k(jokes) dataset from above packages
```{r}

# Matrix of 5000 user rated 100 jokes between +10 to -10
data("Jester5k")

# Real rating matrix is very compact as compared to default R matrix class
nratings(Jester5k)

class(Jester5k)

```

## recommender matrix vs R default matrix 
```{r}

size1 = object.size(Jester5k)
size2 = object.size(as(Jester5k, "matrix"))
ratio = size2/size1;

```

## Lets see why we should be having matrix format as compared to other format 
```{r}

# As Dataframe
head(as(Jester5k, "data.frame"))

# As matrix 
head(as(Jester5k, "matrix"))[, 1:10]


```

## Visual representation of data 
```{r}

hist(getRatings(Jester5k), breaks = 100)

hist(getRatings(normalize(Jester5k)), breaks = 100)

```


## Various modeling tecniques available in recommenderlab package
```{r}

recommederlab = recommenderRegistry$get_entries(datatype = "realRatingMatrix")
names(recommederlab)

```


# Building UBCF Model 

## Training and testing datasets
```{r}

library(caTools)
set.seed(3)
index = sample(x=c(TRUE,FALSE), nrow(Jester5k), prob = c(0.8, 0.2), replace = TRUE)

jester_train = subset(Jester5k, index == TRUE)
jester_test = subset(Jester5k, index == FALSE)

dim(Jester5k)
dim(jester_train)
dim(jester_test)
```

## Building UBCF 
```{r}

ubcf_model = Recommender(jester_train, method = "UBCF")
ubcf_model

```

## Find the recommender jokes(10 nos) by each user 
```{r}

ubcf_pred = predict(ubcf_model, newdata = jester_test, n=10)
ubcf_pred 

```

## Get the list of jokes by each users
```{r}

ubcf_list = sapply(ubcf_pred@items, function(x){colnames(Jester5k)[x]})
ubcf_list[1:10]

```

## List how many recommedation generated for TEST USERS by trained model
```{r}

number_of_jokes = sort(unlist(lapply(ubcf_list, length)), decreasing = TRUE)
table(number_of_jokes)

```

## Evaluate the model 
```{r}

table(rowCounts(Jester5k))

```

###################################################################################

# IBCF Model Generation 

## Filetering Jokes data based on the above observations 
```{r}

# Remove count of jokes above 80 and create a new dataset
model_data = Jester5k[rowCounts(Jester5k)<80]
dim(model_data)

```


## Visual spread of dataset 
```{r}

boxplot(rowMeans(model_data))

boxplot(rowMeans(model_data[rowMeans(model_data) <= 7 & rowMeans(model_data) >-5 ]))

model_data = model_data[rowMeans(model_data) <= 7 & rowMeans(model_data) > -5]
dim(model_data)

```

## Training and Testing Dataset
```{r}

library(caTools)
set.seed(3)

index = sample(x=c(TRUE, FALSE), nrow(model_data), prob = c(0.8,0.2), replace = TRUE)

model_train = subset(model_data, index == TRUE)
model_test = subset(model_data, index == FALSE)

dim(model_data)
dim(model_train)
dim(model_test)

```

## IBCF MODEL
```{r}

ibcf_model = Recommender(model_train, method = "IBCF", parameter = list(k = 30)) # K number of neighbours
ibcf_model

ibcf_model_details = getModel(ibcf_model)
str(ibcf_model_details)

```


## Find the recommendation prediction by test users 
```{r}

ibcf_pred = predict(ibcf_model, model_test, n=5)
# number of recommendation to be generated by each user
ibcf_pred

slotNames(ibcf_pred)

first_user = ibcf_pred@items[[1]]
jokes_by_first_user = ibcf_pred@itemLabels[first_user]


```
















































































































































