---
title: "Sentiment_Analysis"
author: "Echo"
date: "17/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#################################################################################################################################################################

# Sentiment Analysis 

#################################################################################################################################################################

# Load the tweets data : Apple data
```{r}

# setwd()

tweets.df = read.csv("tweets.csv")
str(tweets.df)
tweets.df$created = as.Date(tweets.df$created, format = "%m/%d/%Y")
tweets.df$Tweet = as.character(tweets.df$Tweet)

View(tweets.df)

```

#### Cleaning the text data by removing links, tags and delimiters. 
#### Build a Corpus and specify the location to be the character vectors. 
```{r}

library(tm)
# install.packages("gsubfn")
library(gsubfn)
library(lubridate)

myCorpus = Corpus(VectorSource(tweets.df$Tweet))

myCorpus = tm_map(myCorpus, tolower)
head(myCorpus[[1]])

myStopwords = c((stopwords('english')), c("apple", 
                                          "apples",
                                          "com",
                                          "twitter",
                                          "u",
                                          "de",
                                          "can",
                                          "get",
                                          "app",
                                          "rt",
                                          "iphones",
                                          "iphone",
                                          "new",
                                          "pic",
                                          "s",
                                          "http"))


myCorpus = tm_map(myCorpus, removeWords, myStopwords)
  
removeSingle <- function(x) gsubfn(".", 
                                   list("-" = " ", 
                                        "!" = " ",
                                        "#"=" ",
                                        ","=" ",
                                        "."=" ",
                                        ";"=" ",
                                        "?"=" ",
                                        "@"=" ",
                                        ":"=" ",
                                        "\""=" ",
                                        "&"=" ",
                                        "'"=" ",
                                        "("=" ",
                                        ")"=" ",
                                        "{"=" ",
                                        "}"=" "), x)

myCorpus = tm_map(myCorpus, content_transformer(removeSingle))
myCorpus = tm_map(myCorpus, removePunctuation)
myCorpus = tm_map(myCorpus, stripWhitespace)

```

# Creating a word cloud 
```{r}

library(wordcloud)
library(RColorBrewer)

dtm = DocumentTermMatrix(myCorpus, control = list(wordLengths = c(1, Inf)))

dtm = removeSparseTerms(dtm, 0.99)

word.freq = sort(colSums(as.matrix(dtm)), decreasing = F)
pal = brewer.pal(8, "Dark2")
wordcloud(words = names(word.freq), freq = word.freq, min.freq = 2, random.order = F, colors = pal, max.words = 100 )

```


# Based  on alg0's available in the packages 
```{r}

cleanedTweets = data.frame(Tweets = sapply(myCorpus, as.character), stringsAsFactors = FALSE)
head(cleanedTweets)

# install.packages("syuzhet")
library(syuzhet)

mysentimentvalue = data.frame(get_sentiment(cleanedTweets$Tweets))
colnames(mysentimentvalue) = "polarity"
head(mysentimentvalue)
mysentimentvalue$date = tweets.df$created 

result = aggregate(polarity ~ date, data = mysentimentvalue, sum)
plot(result, type = "l")

```


##### sentiment Analysis: Plot by date - understanding average sentiment score movement 
```{r}

result1 = aggregate(polarity~date, data = mysentimentvalue, mean)
plot(result1, type = "l")

```


# Find the emotional valence association with tweets

```{r}

library(syuzhet)

mysentiment = get_nrc_sentiment(cleanedTweets$Tweets)
class(mysentiment)
View(mysentiment)
cleanedTweets[1103, ]

# Get the sentiment score for each emotion
mysentiment.anger = mean(mysentiment$anger)
mysentiment.anticipation = mean(mysentiment$anticipation)
mysentiment.positive =mean(mysentiment$positive)
mysentiment.disgust = mean(mysentiment$disgust)
mysentiment.fear = mean(mysentiment$fear)
mysentiment.joy = mean(mysentiment$joy)
mysentiment.sadness = mean(mysentiment$sadness)
mysentiment.surprise = mean(mysentiment$surprise)
mysentiment.trust = mean(mysentiment$trust)
mysentiment.negative = mean(mysentiment$negative)

# Create the bar plot

yAxis = c(mysentiment.anger,
          mysentiment.anticipation,
          mysentiment.disgust,
          mysentiment.fear,
          mysentiment.joy,
          mysentiment.negative,
          mysentiment.positive,
          mysentiment.sadness,
          mysentiment.surprise,
          mysentiment.trust
          )

xAxis = c("Anger", "Anticipation", "Disgust", "Fear", "Joy", "Negative", "Positive", "Sadness", "Surprise", "Trust")
colors = c("red", "blue", "orange", "red", "green", "red", "green", "orange", "blue", "green") 
yRange = range(0, yAxis)

barplot(yAxis, names.arg = xAxis, xlab = "Emotional Valence", ylab = "Score", main = "Twitter sentiment", sub = "Apple iphone Launch",
        col = colors, border = "black", xpd = F, ylim = yRange, axisnames = T, cex.axis = 0.8, col.sub = "blue")

```




























































































































































