---
title: "TimeSeries_Forecasting"
author: "Echo"
date: "17/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the libraries and import the required dataset 
```{r}

# install.packages("forecast")
library(forecast)
# install.packages("tseries")
library(tseries)
# install.packages("TSA")
library(TSA)
# install.packages("timeSeries")
library(timeSeries)

milk_demand = read.csv("monthly-milk-production-pounds-p.csv", header = FALSE)
head(milk_demand)
tail(milk_demand)

```


# Convert data into a time series object/format 
```{r}

milk_demand_ts = ts(milk_demand, frequency = 12)

```

# Visualize the time series data 
```{r}

par(mfrow = c(1,1))
plot(milk_demand_ts[,2])

```

# Understanding Airline Passenger data 
```{r}

# data("AirPassengers")
airlinePassenger = read.csv("airline.csv", header = TRUE)
head(airlinePassenger)

```


# convert airline data to time Series object 
```{r}

airlinePassenger.ts = ts(airlinePassenger,
                         start = c(1949, 1), end = c(1960,12),
                         frequency = 12
                         )

plot(airlinePassenger.ts[,2], col = "blue")

```

# De-trending process or converting into a stationary time series 
```{r}

detrended_passengers = diff(airlinePassenger.ts[,2])
plot(detrended_passengers, col = "blue" )

head(detrended_passengers)
# auto correlation factor - q
acf(detrended_passengers)

# partial auto correlation factor - p
pacf(detrended_passengers)

```


# Creating the auto-arima model 
```{r}

library(forecast)
model = auto.arima(airlinePassenger.ts[, 2])

model2 = Arima(airlinePassenger.ts[, 2], order = c(1,0,1))
model3 = Arima(airlinePassenger.ts[, 2], order = c(1,1,1))
model4 = Arima(airlinePassenger.ts[, 2], order = c(1,1,0))
model5 = Arima(airlinePassenger.ts[, 2], order = c(2,1,1), seasonal = c(0,1,0))


par(mfrow = c(2,2))
plot(forecast(model, h = 12))
plot(forecast(model2, h = 12))
plot(forecast(model3, h = 12))
plot(forecast(model4, h = 12))
plot(forecast(model5, h = 12))

```


############################################################################################################################################

# Exponential Time Series (ETS)
Types of ETs forecasting techniques are:
1. Single Smoothing Exponential model (when stationary) : use DMA
2. Double Smoothing Exponential model (when has trend) : use Holt's method
3. Triple Smoothing Exponential model (when has trend and seasonality) : Use Holt's-Winter method

# Understanding the components of time series 
```{r}

decompose_passenger = decompose(airlinePassenger.ts[, 2])
plot(decompose_passenger)

```
Observations :
1. Uptrending 
2. Have Seasonality
3. also, has white noise(randomness)

# Let's apply Holts-winter method
```{r}

holtswinter_model = HoltWinters(airlinePassenger.ts[, 2]) 

forecasted_ets = forecast(holtswinter_model, 12)

plot(forecasted_ets)
```






















































