---
title: "Unsupervised_Learning"
author: "Echo"
date: "09/02/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ACQUIRING THE DATA
```{r}

# setwd()
movie_data = read.csv("movie_metadata.csv", header = TRUE) 

names(movie_data)
str(movie_data)
summary(movie_data)

```


# Problem Statements:
1. Rate/Rank the directors based on the movies's budget and gross collection.

```{r}


Budg_Collect_DS = movie_data[, c("director_name", "movie_title", "budget", "gross")]
anyNA(Budg_Collect_DS)
Budg_Collect_DS = na.omit(Budg_Collect_DS)

dim(Budg_Collect_DS)
names(Budg_Collect_DS)

scaled_DS = scale(Budg_Collect_DS[, -(1:2)])
dim(scaled_DS)

```


##################################################################################################################################################
# K-Mean Clustering :

## How to identify the optimal clusters/groups ?
```{r}
# install.packages("factoextra")
library(factoextra)

fviz_nbclust(scaled_DS, kmeans, method = "wss")+
  #geom_vline(xintercept = 3, linetype = 2)+
  labs(subtitle = "Elbow_Scree method")

```


## How to identify the optimal clusters/groups ? (PPT Method)
```{r}
## How to identify the optimal clusters/groups ?
# wssplot <- function(data, nc=15, seed=1234){
#   wss <- (nrow(data)-1)*sum(apply(data,2,var))
#   for (i in 2:nc){
#     set.seed(seed)
#     wss[i] <- sum(kmeans(data, centers=i)$withinss)}
#   plot(1:nc, wss, type="b", xlab="Number of Clusters",
#        ylab="Within groups sum of squares")
#   }
# 
#  wssplot(scaled_DS, nc=7)
#  abline(v=3,lty=3)
```


## K Mean Clustering model
```{r}

clustering_DS = kmeans(scaled_DS, centers = 3)
names(clustering_DS)
head(clustering_DS$cluster)
head(scaled_DS)

Budg_Collect_DS$cluster_kmeans = clustering_DS$cluster
str(Budg_Collect_DS)
head(Budg_Collect_DS)

# finding out the top 10 rows of each cluster
head(Budg_Collect_DS[Budg_Collect_DS$cluster_kmeans==1,],10)
head(Budg_Collect_DS[Budg_Collect_DS$cluster_kmeans==2,],10)
head(Budg_Collect_DS[Budg_Collect_DS$cluster_kmeans==3,],10)

```


## Profiling-K Means :
`Data profiling is a technique used to analyze and gain a better understanding of raw data. It is the first step in determining what insights data can yield when you run it through machine learning algorithms in order to make predictions.`
```{r}
aggr = aggregate(Budg_Collect_DS[, -c(1:2)], list(Budg_Collect_DS$cluster_kmeans), mean)
class(aggr)

aggr$min = aggregate(Budg_Collect_DS[, -c(1:2)], list(Budg_Collect_DS$cluster_kmeans), min)
aggr$max = aggregate(Budg_Collect_DS[, -c(1:2)], list(Budg_Collect_DS$cluster_kmeans), max)

head(aggr)

as.vector(aggr$min)
as.vector(aggr$max)

clus.profile = data.frame( cluster = aggr[ ,1],
                           Freq = as.vector(table(Budg_Collect_DS$cluster_kmeans)),
                           aggr[,-1])

clus.profile$budget = clus.profile$budget/1000000
clus.profile$gross = clus.profile$gross/1000000

clus.profile

```




#############################################################################################################################
# C-Means Clustering
```{r}

names(Budg_Collect_DS)

```

## C Mean clustering Model
```{r}
library(e1071)

cluster_cmean = cmeans(scaled_DS, 3)
names(cluster_cmean)
head(cluster_cmean$membership)
head(cluster_cmean$cluster)

cluster_cmean$size

Budg_Collect_DS$cluster_cmean = cluster_cmean$cluster

head(Budg_Collect_DS[Budg_Collect_DS$cluster_cmean == 1,],10)
head(Budg_Collect_DS[Budg_Collect_DS$cluster_cmean == 2,],10)
head(Budg_Collect_DS[Budg_Collect_DS$cluster_cmean == 3,],10)

```

## Profiling C Means :
```{r}
names(Budg_Collect_DS)

aggr = aggregate(Budg_Collect_DS[, -c(1:2,5)], list(Budg_Collect_DS$cluster_cmean), mean)

clus.profile_cmeans = data.frame( cluster = aggr[,1],
                                  Freq = as.vector(table(Budg_Collect_DS$cluster_cmean)),
                                  aggr[,-1]
                                )

clus.profile_cmeans

clus.profile_cmeans$budget = clus.profile_cmeans$budget/1000000
clus.profile_cmeans$gross = clus.profile_cmeans$gross/1000000

clus.profile_cmeans

```



#########################################################################################################################
# Hierarchical Clustering :

## Distance Calculation 
```{r}
names(Budg_Collect_DS)
dim(Budg_Collect_DS)

# subsetting our data frame as hierarchical clustering is not a good idea for large data sets
subset_mov = scaled_DS[1:20, ]
class(subset_mov)

row.names(subset_mov) = Budg_Collect_DS[1:20, "director_name"]

distance = dist(as.matrix(subset_mov))
distance

```


## Find H clustering
```{r}
hc = hclust(distance)

plot(hc)
rect.hclust(hc, k=4, border = "red")
```

























































